High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-11-09 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present new high resolution ($\sim$50\,mas) ALMA observations of the 1.3\,mm continuum. The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source. The new ALMA data reveal a very thin ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 3.86$\pm$1.00\,au. Ring13 is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail. The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc. Faint mm-continuum close ($\sim0\farcs02$) to the stellar position is picked up by ALMA. ***
  %coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. 
  The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model. The surprisingly thin Ring13 is nonetheless roughly 12 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. 
\end{abstract}

@@

For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights. The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required. Here we adopted a $\chi^2$ model image with $\lambda$ = 0.1 for regularization. The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc. This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e. Ring13 at 13\,au and Ring24 starting at 24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between
$\sim$10 and 17\,au.

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc. Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs077 \, \times \, 0\farcs051$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs026 \, \times \, \sim0\farcs017$). The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The orange ellipse shows the size of the beam: $0\farcs026 \, \times \, 0\farcs017$. For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}). We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.06\pm0.04$\,mas, relative to the stars.

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of 13.46$\pm$0.43\,au (See Fig.~\ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs077 \,\times \, 0\farcs051$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs026 \, \times \, \sim0\farcs016$), the ring width is $\sim$3.86$\pm$1.00\,au.

Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars. We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star. Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.

@@

The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-
sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.

The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 254\,$\degr$, east of north. Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 347\,$\degr$. There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA. This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.

@@

For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two Gaussian profiles. In an effort to recreate the break seen in the outer ring between 30.2 and 36.7\,au, we chose a different value for $\gamma$ = -6. For the large dust grains the surface density profile is thus
\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] + \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

The inner part of the outer ring follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, marking the beginning and the maximum density peak of the outer ring respectively, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
$R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, with $R_\mathrm{in}$ = 20.5\,au and $R_\mathrm{peak}$ = 25\,au for the small dust grains and $R_\mathrm{in}$ = 22\,au and $R_\mathrm{peak}$ = 27.7\,au for the large dust grains. This parameter allow us to model a smoother inner wall of the outer ring.

@@

The gas and small dust surface density profiles begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.1\,au. For the small dust grains, we propose a three ringed structure. The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.~\ref{sec:Observations}, is not detectable in the IRDIS observations but was required to account for the SED. Then follow the two rings observed by IRDIS: Ring13, from 12 to 19.5\,au, which is surrounded by very narrow 1\,au-wide gap, and then Ring24, that starts 20.5\,au and has its maximum density peak at 25\,au. The small-dust density then decays exponentially with radius.

@@

The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable. We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 33.9\,$\degr$ and a P.A. = 74.6\,$\degr$. Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.

@@

Our parametric model is fairly successful in reproducing the available data. The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.

@@

The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24. As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a good approximation of the disc structure, including the dimensions of Ring13. Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.6\,au, a width of 3.7\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.28 to 0.40\,au. The total dust mass of Ring13 is about 3\,M$_{\earth}$ in the model. In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$35\,au, as in the observations, and has a total dust mass of $\sim$43\,M$_{\earth}$. The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.14\,au difference in the centroid location of the ring, and a 0.17\,au difference in the width estimation.
%As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
Using the parametric model scale height of 0.33\,au at 13.46\,au and the measured width of Ring13 (3.86\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$12 times its scale height.

The observed structure may point to the existence of planet-disk interaction within this system, where a giant planet depletes its orbit of gas and dust material. A possible constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24. This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets. We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.

The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 3.86\mathrm{au}$. The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$. Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution. Assuming that the gas' Ring13-width in the RT model corresponds to the FWHM of a Gaussian structure $w_\mathrm{g} = 7.5\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.

Similarly to \citet{2018ApJ...869L..46D}, the ratio between dust and gas ring width can be linked to important properties:
\begin{equation}\label{eq:ringwidth}
        \frac{w_\mathrm{d}}{w_\mathrm{g}} = \sqrt{\frac{\alpha}{\alpha+\mathrm{St}}}\,,
\end{equation}
where we implicitly assumed the turbulent diffusivity to be equal to the turbulent viscosity. Here, $\alpha$ represents the typical parameter for turbulent viscosity, and $\mathrm{St}$ is the dimensionless Stokes number. Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$. With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.01$ for the level of turbulent viscosity. We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.

>>>>

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present new high resolution ($\sim$50\,mas) ALMA observations of the 1.3\,mm continuum. The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source. The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail. The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc. Faint mm-continuum close ($\sim0\farcs02$) to the stellar position is picked up by ALMA. ***
  %coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. 
  The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model. The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. 
\end{abstract}

@@

For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights. The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required. Here we adopted a $\chi^2$ model image with $\lambda$ = 0.01 for regularization (***mem\_lS0.01\_lL0.0\_nogrid/mod\_out.fits). The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc. This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e. Ring13 at 13\,au and Ring24 starting at 24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc. Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$). The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The orange ellipse shows the size of the beam: $0\farcs035 \, \times \, 0\farcs031$. For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}). We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 77.31$\pm$0.03\,$\degr$, an inclination of 32.96$\pm$0.02\,$\degr$ and a centre at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas, relative to the stars.

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 2.87$\pm$0.50\,au, and a stellocentric radius of 13.32$\pm$0.26\,au (See Fig.~\ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.

Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star. Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.

@@

The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.

The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 265\,$\degr$, east of north. Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of $\sim$80\,$\degr$. There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA. This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.

@@

For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two Gaussian profiles. In an effort to recreate the break seen in the outer ring between 29.8 and 37.9\,au, we chose a different value for $\gamma$ = -3. For the large dust grains the surface density profile is thus
\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] + \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

The inner part of the outer ring follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, marking the beginning and the maximum density peak of the outer ring respectively, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
$R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, with $R_\mathrm{in}$ = 19.5\,au and $R_\mathrm{peak}$ = 25\,au for the small dust grains and $R_\mathrm{in}$ = 24.2\,au and $R_\mathrm{peak}$ = 26.6\,au for the large dust grains. This parameter allow us to model a smoother inner wall of the outer ring.

@@

The gas and small dust surface density profiles begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au. For the small dust grains, we propose a three ringed structure. The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.~\ref{sec:Observations}, is not detectable in the IRDIS observations but was required to account for the SED. Then follow the two rings observed by IRDIS: Ring13, from 12 to 19.5\,au, %which is surrounded by very narrow 1\,au-wide gap, 
and then Ring24, that starts 19.5\,au and has its maximum density peak at 25\,au. The small-dust density then decays exponentially with radius.

@@

The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable. We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A. = 77.31\,$\degr$. Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.

@@

While certainly not unique, our parametric model is fairly successful in reproducing the available data. The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.

@@

The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24. As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a good approximation of the disc structure, including the dimensions of Ring13. Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.35\,au, a width of 2.1\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.30 to 0.36\,au. The total dust mass of Ring13 is about 3\,M$_{\earth}$ in the model***. In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$35\,au, as in the observations, and has a total dust mass of $\sim$43\,M$_{\earth}$. The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.03\,au difference in the centroid location of the ring, and a 0.6\,au difference in the width estimation.
%As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
Using the parametric model scale height of 0.33\,au at 13.32\,au and the measured width of Ring13 (1.50\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$4.6 times its scale height.

The observed structure may point to the existence of planet-disk interaction within this system, where a giant planet depletes its orbit of gas and dust material. A possible constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24. As \citet{Ru_z_Rodr_guez_2019} suggests, the planet between Ring13 and Ring24 may be a Jovian-mass planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$. This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets. We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.

The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$. The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$. Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution. Assuming that the gas' Ring13-width in the RT model corresponds to the FWHM of a Gaussian structure $w_\mathrm{g} = 7.5\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.

Similarly to \citet{2018ApJ...869L..46D}, the ratio between dust and gas ring width can be linked to important properties:
\begin{equation}\label{eq:ringwidth}
        \frac{w_\mathrm{d}}{w_\mathrm{g}} = \sqrt{\frac{\alpha}{\alpha+\mathrm{St}}}\,,
\end{equation}
where we implicitly assumed the turbulent diffusivity to be equal to the turbulent viscosity. Here, $\alpha$ represents the typical parameter for turbulent viscosity, and $\mathrm{St}$ is the dimensionless Stokes number. Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$. With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.001$ for the level of turbulent viscosity. We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.
